Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-05 sections/tensors.tex
Update on Overleaf.

\begin{figure}[ht]
\footnotesize
\begin{tabular} {|c|p{0.65\linewidth}|} 
    \hline
    $declare(lvl, init, dims...)$ & Declares the level to hold subtensors of size $dims$ and an initial value of $init$. Requires the level to be in
read-only mode.\\
\hline
$freeze(lvl)$ & Finalizes the updates in the level, and readies the
level for reading. Requires the level to be in update-only mode.\\
\hline
$thaw(lvl)$ & Prepares the level to accept updates. Requires the level
to be in read-only mode.\\
\hline
$unfurl(fiber(lvl, pos),$

$ [ext], mode, [op], [rhs])$ & When $ext$ is given, unfurls the fiber at position
$pos$ in the level $lvl$ over the extent $ext$. When $mode = \finchread$,
returns a looplet nest over the values in the read-only fiber.  When $mode =
\finchupdate$, returns a looplet nest over mutable subfibers in the update-only
fiber. When applied to a scalar or leaf node, $ext$ is omitted and we may also use $op$ and $rhs$ to update the scalar value. Often, skipping over mutable locations allows the level to know which
locations must be stored. Often, a dirty bit may be used in $tns$ to communicate
whether the mutable subfiber has been written to, which allows the parent fiber
to know whether the subfiber must be stored explicitly.\\
\hline
$assemble(lvl, pos_{start}, pos_{stop})$& Allocates subfibers in the
level from positions $pos_{start}$ to $pos_{stop}$. Usually, this function is
only ever called on unassembled positions, but some levels (such as dense levels
or bytemaps) may support reassembly.\\
\hline
    \end{tabular}

>>>>

\begin{figure}[ht]
\footnotesize
\begin{tabular} {|m{5em}|p{0.65\linewidth}|} 
    \hline
    $declare(lvl,$\newline{}$ init, dims...)$ & Declares the level to hold subtensors of size $dims$ and an initial value of $init$. Requires the level to be in
read-only mode.\\
\hline
$freeze(lvl)$ & Finalizes the updates in the level, and readies the
level for reading. Requires the level to be in update-only mode.\\
\hline
$thaw(lvl)$ & Prepares the level to accept updates. Requires the level
to be in read-only mode.\\
\hline
$unfurl($\newline{}$fiber(lvl, pos),$\newline{}$ [ext], mode,$ \newline{} $[op], [rhs])$ & When $ext$ is given, unfurls the fiber at position
$pos$ in the level $lvl$ over the extent $ext$. When $mode = \finchread$,
returns a looplet nest over the values in the read-only fiber.  When $mode =
\finchupdate$, returns a looplet nest over mutable subfibers in the update-only
fiber. When applied to a scalar or leaf node, $ext$ is omitted and we may also use $op$ and $rhs$ to update the scalar value. Often, skipping over mutable locations allows the level to know which
locations must be stored. Often, a dirty bit may be used in $tns$ to communicate
whether the mutable subfiber has been written to, which allows the parent fiber
to know whether the subfiber must be stored explicitly.\\
\hline
$assemble(lvl, pos_{start}, pos_{stop})$& Allocates subfibers in the
level from positions $pos_{start}$ to $pos_{stop}$. Usually, this function is
only ever called on unassembled positions, but some levels (such as dense levels
or bytemaps) may support reassembly.\\
\hline
    \end{tabular}
